---
format: 
  revealjs:
    incremental: true
    slide-number: true
    progress: true
    code-line-numbers: true
    code-copy: true
    theme: 
      - midquarter-survey.scss
    embed-resources: true
---

##  {#title-slide data-menu-title="Title Slide" background="#cad2c5"}

[MEDS Mid-quarter Survey Results]{.custom-title}

<hr class="hr-off-white">

[Winter Quarter]{.custom-subtitle}


##  {#Survey-Participation data-menu-title="Survey Participation"}

[Participation]{.slide-title}

<hr>

-   11/30 MEDS Students completed the survey
-   No non MEDS students completed the survey


##  {#ML-results data-menu-title="Machine Learning Couse Results"}

[EDS 232: Machine Learning]{.slide-title}

<hr>

```{r}
#| eval: true
#| echo: false
library(ggplot2)
library(tidyverse)
library(ggthemes)
library(cowplot)
survey_results <- read.csv(here::here("mid-quarter-survey-winter.csv"))
colnames(survey_results) <- c("date", "Meds_student_y/n", "eds232_enrolled", "eds232_pace", "eds232_homeworks", "eds232_discussion", "eds232_textbook", "eds232_other", "eds240_enrolled", "eds240_lecture", "eds240_discussion", "eds240_homework", "eds240_other", "eds241_enrolled", "eds241_lecture", "eds241_homeworks", "eds241_other", "capstone_enrolled", "capstone_feeling", "capstone_speakers", "capstone_comments", "additional_feedback")

```

```{r}
eds232_pace <- ggplot(data = survey_results %>% 
         mutate(eds232_pace = factor(eds232_pace, levels = c(1, 2, 3), labels = c("Too slow", "Just right", "Too fast"))), 
       aes(x = eds232_pace)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Lecture Pace") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()
eds232_discussion <- ggplot(data = survey_results %>% 
         mutate(eds232_discussion = factor(eds232_discussion, levels = c(1, 2, 3), labels = c("Not useful", "Useful", "Very useful"))), 
       aes(x = eds232_discussion)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Discussion") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()
plot_grid(eds232_pace , eds232_discussion , nrow = 2, scale = 0.95)

```






##  {#ML-results data-menu-title="Machine Learning Couse Results"}

[EDS 232: Machine Learning]{.slide-title}
<hr>
```{r}

#| eval: true
#| echo: false

eds232_homeworks <- ggplot(data = survey_results %>% 
         mutate(eds232_homeworks = factor(eds232_homeworks, levels = c(1, 2, 3), labels = c("Too easy", "Just right", "Too hard"))), 
       aes(x = eds232_homeworks)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Homework Difficulty") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()




eds232_textbook <- ggplot(data = survey_results %>% 
         mutate(eds232_textbook = factor(eds232_textbook, levels = c(1, 2, 3), labels = c("Not useful", "Useful", "Very useful"))), 
       aes(x = eds232_textbook)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Textbook Usefulness") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()


plot_grid(eds232_homeworks , eds232_textbook , nrow = 2, scale = 0.95)

```




##  {#Policy-results data-menu-title="Policy Evaluation Course Results"}

[EDS 241: Environmental Policy Evaluation ]{.slide-title}

<hr>

```{r}
eds241_lecture <- ggplot(data = survey_results %>% 
         mutate(eds241_lecture = factor(eds241_lecture, levels = c(1, 2, 3), labels = c("Too slow", "Just right", "Too fast"))), 
       aes(x = eds241_lecture)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Lecture Pace") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()

eds241_homeworks <- ggplot(data = survey_results %>% 
         mutate(eds241_homeworks = factor(eds241_homeworks, levels = c(1, 2, 3), labels = c("Too easy", "just right", "Too hard"))), 
       aes(x = eds241_homeworks)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Homework Difficulty") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()


plot_grid(eds241_lecture , eds241_homeworks , nrow = 2, scale = 0.95)

```



##  {#Data-Viz-results data-menu-title="Data Visualization Course Results"}

[EDS 240: Data Visualization and Communication ]{.slide-title}

<hr>


```{r}
eds240_lecture <- ggplot(data = survey_results %>% 
         mutate(eds240_lecture = factor(eds241_lecture, levels = c(1, 2, 3), labels = c("Too slow", "Just right", "Too fast"))), 
       aes(x = eds240_lecture)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Lecture Pace") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()

eds240_discussion <- ggplot(data = survey_results %>% 
         mutate(eds240_discussion = factor(eds240_discussion, levels = c(1, 2, 3), labels = c("Not useful", "Useful", "Very useful"))), 
       aes(x = eds240_discussion)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Discussion") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()



plot_grid(eds240_lecture , eds240_discussion , nrow = 2, scale = 0.95)
```

##  {#Data-Viz-results data-menu-title="Data Visualization Course Results"}

[EDS 240: Data Visualization and Communication ]{.slide-title}

<hr>


```{r}
eds240_homeworks <- ggplot(data = survey_results %>% 
         mutate(eds240_homework = factor(eds240_homework, levels = c(1, 2, 3), labels = c("Too easy", "just right", "Too hard"))), 
       aes(x = eds240_homework)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "Homework Difficulty") +
  scale_x_discrete(drop =FALSE)+ 
  theme_fivethirtyeight()


eds240_homeworks

```

##  {#Capstone-results data-menu-title="Capstone Course Results"}

[EDS 411A: Capstone Project ]{.slide-title}
<hr>


```{r}
capstone_feeling <- ggplot(data = survey_results %>% 
         mutate(capstone_feelings = factor(capstone_feeling, levels = c(1, 2, 3, 4, 5), labels = c("1", "2", "3", "4", "5"))), 
       aes(x = capstone_feelings)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "How students are feeling about capstone course") +
  scale_x_discrete(drop = FALSE) + 
  theme_fivethirtyeight()

capstone_speakers <- ggplot(data = survey_results %>% 
         mutate(capstone_speakers = factor(capstone_speakers, levels = c(1, 2, 3, 4, 5), labels = c("1", "2", "3", "4", "5"))), 
       aes(x = capstone_speakers)) + 
  geom_bar(width = 1/3, fill = "#84a98c") + 
  labs(x = element_blank(), y = "Number of Responses", title = "How useful have speakers been") +
  scale_x_discrete(drop = FALSE) + 
  theme_fivethirtyeight()
plot_grid(capstone_feeling, capstone_speakers, nrow = 2, scale = 0.95)
```


##  {#other-notes data-menu-title="Other Notes"}

[Other Notes!]{.slide-title}

<hr>

- Standard of markdown & comments
- Git conflicts 
- Student engagement on Tuesdays vs Thursdays
- Engagement with research papers/ case studies
- General streamlining of best practices 
  - Naming convention for dataframes
  - Commenting code
  - Data visualization expectation
  - Copying/ pasting of assignment questions
  

##  {#final-slide data-menu-title="Thanks!" background="#cad2c5"}

[Thank you for listening!]{.custom-title}
